%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[9pt]{basecv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.4\textwidth}
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    { \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{William White}}}} % First name

    \vspace{6pt}

    {\Large Senior Software Engineer} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.19\textwidth} % 20% of the page width for the first row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
    \icon{Globe}{11}{\href{https://willwhite.dev}{willwhite.dev}}\\
    \icon{Phone}{11}{\href{tel:281-658-0534}{(281) 658-0534}}\\
    \icon{MapMarker}{11}{Aurora, Colorado}\\
\end{minipage}
\begin{minipage}[t]{0.28\textwidth} % 27% of the page width for the second row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    \icon{Envelope}{11}{\href{mailto:contact@willwhite.dev}{contact@willwhite.dev}}\\
    \icon{Github}{11}{\href{https://github.com/will-white}{github.com/will-white}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/william-white-76068893/}{/in/william-white-76068893}}\\
\end{minipage}
%----------------------------------------------------------------------------------------
%	SUMMARY, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.4\textwidth}
    \cvsect{Summary}\\
    Polyglot Software Engineer with 10+ years of demonstrated industry experience with a keen eye of UX and a passion for DevOps / infrastructure. Who has developed an array of web, desktop, batch, and business intelligence solutions, of all sizes. Successful in developing simple solutions for complex problems, optimizing business procedures, processes, and productivity.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.57\textwidth}
    \cvsect{Skills}
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        CSharp (C\#), TypeScript, JavaScript, Python, Java, LINQ, SQL, SOAP, JSON, XML, HTML, CSS, LESS, SASS
    \end{minipage}
    \vspace{3.5mm}\\
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Frameworks:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        React, React Query, Redux, Angular 2+, Node.js, OpenFAAS, Karma, Jest, DevExpress, MUI, Material, Bootstrap, Tailwind
        \\
        .NET, .Net Core, EF, WCF, WPF, MSTest, xUnit, NUnit
    \end{minipage}
    \vspace{3.5mm}\\
    \begin{minipage}[t]{0.21\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        AWS, Aurora, RDS, SQS, DynamoDB, S3, Lambda, SNS, CloudFront, GCP App Engine, Address, Geocoding, GIS,
        Docker, Kubernetes, RabbitMQ, SSMS, MSSQL, MySQL, PostgreSQL, MongoDB
    \end{minipage}
    {\vspace{2mm}}
\end{minipage}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\cvsect{Experience}
{\vspace{-10pt}}
\begin{entrylist}
    \entry
    {3/2022 -- 3/2024}
    {Senior Software Engineer}
    {SkySlope Inc.}
    {\vspace{-9pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Developed, reviewed, and maintained, key fullstack business application with over 2000 unit tests, and 30 pull requests per sprint. While still delivering weekly to bi-weekly product releases.
            \item Helped monitor, debug, triage, mitigate, and operate, several applications with over 10 thousand daily concurrent users.
            \item Participated and facilitated importing of 100s of thousands users from external integrators, via SSO, and private standalone accounts.
            \item Enhanced app experience for monetization purposes with sponsored/partnered ADs without impeding user interactions or performance with app
            \item Lead initiative to reduce cluster cost by moving to file and data streaming, and deferred executions.
            \item Collaborated and worked with half a dozen teams to create one of the most adopted prop tech app.
        \end{itemize}
    }
    \entry
    {8/2020 -- 3/2022}
    {Senior Software Engineer}
    {ARMtech Insurance Services Inc.}
    {\vspace{-9pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Developed unified single sign on solution using Angular 2+, Node.js, .NET Core, and Duo Security.
            \item Refactored dozens of MSSQL PDF Reports to DevExpress and Angular/HTML based ones.
            \item Improved coding standards with use of ESLint, Prettier, and CI/CD scripts using GitLab CI/CD.
        \end{itemize}
    }
    \entry
    {8/2014 -- 8/2020}
    {Software Engineer}
    {ARMtech Insurance Services Inc.}
    {\vspace{-9pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Spearheaded performance, and refactoring of core business service that lead to a 45x up lift
            \item Implemented use of customized Webpack Hot Module Reloading saving countless hours of development
                  and debugging time across all teams.
            \item Built a web-based SaaS B2B application utilizing Angular 2+, Node.js, WCF, RabbitMQ, Redis, CouchDB,
                  Entity Framework, MSSQL, Docker, and DevExpress Reporting.
            \item Developed and optimized customized business software solutions that helped manage risk more
                  effectively and save tens of millions in capital per quarter.
        \end{itemize}
    }
\end{entrylist}
%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
    {Fullstack App\\\footnotesize{etsy-a-like}}
    {Ecommerce Site}
    {\href{https://github.com/will-white/ecommorg}{github link}}
    {Etsy alike Ecommerce website built with React front end with Swipe integrations and a NestJS REST like backend, PostgreSQL DB, utilizing RabbitMQ for asynchronous integration events. Project repository uses Nrwl monorepo with GitHub CI/CD to automatically test and deploy all UI and services to a Heroku and GCP cloud infrastructure.}
    \entry
    {}
    {HomeLab}
    {\href{https://github.com/will-white/home-cluster}{github link}}
    {Ever evolving bare metal environment in my server rack fulfilling various purposes; utilizing various IaaS technologies. Fully controlled via GitOps, using Ansible, Proxmox, Kubernetes, Docker, Grafana, Promethus, ELK, and Fluentd.}
    \entry
    {Microservice}
    {USDA RMA Insurance Premium Calculation Engine}
    {\href{https://github.com/will-white/RMA}{github link}}
    {Custom Calculation/Business engine that processes Insurance premiums derived from RMA's agricultural custom premium calculations. Downloads, parses, and converts PDF text calculations into dynamically generated CSharp code}
    % \entry
    % {}
    % {My project 4}
    % {github.com link}
    % {%Dummy text 
    %     \lipsum[1][1-3]}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\cvsect{Education}
\begin{entrylist}
    \entry
    {8/2008 - 12/2013}
    {B.S.E. in Computer Science and Engineering}
    {University of Texas at Arlington}
    {In-Major GPA: 3.4}
\end{entrylist}
%----------------------------------------------------------------------------------------
%	END OF DOCUMENT
%----------------------------------------------------------------------------------------
\end{document}
